Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-28 TACAS2018/paper.tex
abstract

\begin{abstract} 
%
We present a sound and automated approach to synthesizing safe,
digital, observer-based controllers for physical plants represented as
linear, time-invariant models.  Models are defined as differential
equations with inputs, evolving over a continuous state space. The
synthesis accounts for errors caused by the digitization effects
introduced by the controller.  We use an optimization-based
counterexample-guided inductive synthesis (CEGIS) procedure that is
driven by abstraction refinement, where in each iteration we take the
following steps: (1) We start by only considering a low-resolution
discretized model of the system and only static properties, which
enables us to find candidate solutions fast.  (2) Once we have a
candidate, we use matrix eigen-decomposition
and objective functions to iteratively optimize it.
%Whenever the optimization is unable to yield further results, it feeds back to the
%synthesiser in a traditional CEGIS manner.
This design yields a significant speed-up compared to a traditional
CEGIS scheme (i.e. without optimization).  We demonstrate the
practical value of this approach by automatically synthesizing safe
observer-based controllers for physical plant models from the digital
control literature.
%
\end{abstract}

>>>>

\begin{abstract} 
%
We present a sound and automated approach to synthesizing safe,
digital, observer-based controllers for physical plants represented as
linear, time-invariant models.  Models are defined as differential
equations with inputs, evolving over a continuous state space. The
synthesis accounts for errors caused by the digitization effects
introduced by the controller.  We use a counterexample-guided
inductive synthesis procedure enhanced with abstraction
refinement and optimization, which allows us to start by considering
a low-resolution discretized model of the system and %, which enables us to
find candidate solutions fast. This model gets refined on demand.
Moreover, in order to improve our chances of finding a solution even
when considering coarse abstractions of the system, in each iteration of the CEGIS
loop we use matrix eigen-decomposition to optimize our candidate.
%% Once we have a candidate, we use matrix eigen-decomposition
%% and objective functions to iteratively optimize it.
%Whenever the optimization is unable to yield further results, it feeds back to the
%synthesiser in a traditional CEGIS manner.
This design yields a significant speed-up compared to a traditional
CEGIS scheme (i.e. without abstraction refinement and optimization).
We demonstrate the practical value of this approach by automatically
synthesizing safe observer-based controllers for physical plant models
from the digital control literature.
%
\end{abstract}
